How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-08-01 research/paper/draft.tex
some figures updated
added mention of scaling investigation

@@

@@

We achieve this goal by dividing out the true $n(z)$ and multiplying by the 
interim $n(z)$ as in
\begin{align}
\label{eq:transformation}
p(z_{spec} | z_{phot}, \textul{\sigma}, \vec{\phi}_{int}) =& p(z_{spec} | 
z_{phot}, \textul{\sigma}, \vec{\phi}_{true})\ \frac{p(z_{spec} | 
\vec{\phi}_{int})}{p(z_{spec} | \vec{\phi}_{true}},
\end{align}
since $p(z_{spec} | z_{phot}, \textul{\sigma}, \vec{\phi})$ is separable and 
the term $p(z_{spec} | z_{phot}, \textul{\sigma})$ changes independently of the 
$p(z_{spec} | \vec{\phi})$ term.  The information about $\vec{\phi}_{true}$ is 
retained by the elements of the catalog: only $(z_{spec}, z_{phot})$ pairs 
drawn from the true distribution will be represented in the catalog!

>>>>

The tests presented here are conducted with samples of $N = 10^{4}$ with

@@

In comparison with use of the stacked estimator of the redshift distribution 
function, the hierarchical approach is computationally expensive.  In a future 
revision, the \chippr code will be optimized for speed and resource efficiency. 
 At this stage, we establish scaling behavior to project the expense in terms 
of computational resources.

@@

We achieve this goal by dividing out the true $n(z)$ and multiplying by the 
interim $n(z)$ as in
\begin{align}
\label{eq:transformation}
p(z_{spec} | z_{phot}, \textul{\sigma}, \vec{\phi}_{int}) =& p(z_{spec} | 
z_{phot}, \textul{\sigma}, \vec{\phi}_{true})\ \frac{p(z_{spec} | 
\vec{\phi}_{int})}{p(z_{spec} | \vec{\phi}_{true})},
\end{align}
since $p(z_{spec} | z_{phot}, \textul{\sigma}, \vec{\phi})$ is separable and 
the term $p(z_{spec} | z_{phot}, \textul{\sigma})$ changes independently of the 
$p(z_{spec} | \vec{\phi})$ term.  The information about $\vec{\phi}_{true}$ is 
retained by the elements of the catalog: only $(z_{spec}, z_{phot})$ pairs 
drawn from the true distribution will be represented in the catalog!
